An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-04-29 EconGrowth.Rnw
Minor change to a formula.
Edited to-do list.

\item{Heun: Fix weirdnesses with China on the CD gamma grid search graph}

@@

\item Heun: Add CES production function fits

@@

\item{Heun: Deal with missing covariance numbers when columns have unequal length. Use the \texttt{subset} command?}
\item{Heun: Add data from 2011 to the models}

@@

@@

The literature shows three quantifications of energy ($E$) used in energy-augmented production functions: thermal energy ($Q$), exergy ($X$), and useful work ($U$). Thermal energy ($Q$) is the heat content of an energy carrier. Exergy ($X$) is the maximum useful work that can be extracted from an energy carrier by a process that brings the system into equilibrium with a heat reservoir (typically the surrounding environment). Useful work ($U$) includes the direct energy that goes into an economy, including work from machines, human muscles, and animals. Firms pay for thermal energy ($Q$), but useful work ($U$) alters the size and shape of materials, keeps the lights on, and transports goods to consumers. Not all forms of energy are created equal in terms of ability to generate economic activity \citep{Cleveland:2000vl, Warr:2010ht}. Exergy ($X$), and to a greater extent, useful work ($U$) account for the useful energy that goes into generating economic activity, thereby reflecting the ``quality'' of each energy type and the efficiency of machines and devices typically used to convert thermal energy ($Q$) into useful work ($U$).

@@

\begin{equation} \label{eq:human_muscle}
  E_{workers} = (E_{m,workers})(N_{workers})
\end{equation}

>>>>

@@

\item{Heun: Fix the ordering of references in the bibliography by setting the alphabetical order of the keys to match the temporal order of the references.}
\item{Heun: Obtain answers to questions for Caleb.}
\item{Heun: Add references from Lucas.}
\item{Heun: Add CES production function fits}

@@

\item{Heun: Deal with missing covariance numbers when columns have unequal length. Use the \texttt{subset} command? Partially complete: need to work on the $u$ data only.}

@@

\item{\st{Heun: Add data from 2011 to the models}}
\item{\st{Heun: Fix weirdnesses with China on the CD gamma grid search graph.}}

@@

The literature shows three quantifications of energy ($E$) used in energy-augmented production functions: thermal energy ($Q$), exergy ($X$), and useful work ($U$). Thermal energy ($Q$) is the heat content of an energy carrier. Exergy ($X$) is the maximum useful work that can be extracted from an energy carrier by a process that brings the system into equilibrium with a heat reservoir (typically the surrounding environment). Useful work ($U$) includes the direct energy that goes into an economy, including work from machines, human muscles, and animals. Firms pay for thermal energy ($Q$), but useful work ($U$) alters the size and shape of materials, keeps lights on, and transports goods to consumers. Not all forms of energy are created equal in terms of ability to generate economic activity \citep{Cleveland:2000vl, Warr:2010ht}. Exergy ($X$), and to a greater extent, useful work ($U$) account for the useful energy that goes into generating economic activity, thereby reflecting the ``quality'' of each energy type and the efficiency of machines and devices typically used to convert thermal energy ($Q$) into useful work ($U$).

@@

\begin{equation} \label{eq:human_muscle}
  E_{workers} = E_{m,workers} N_{workers}
\end{equation}
